Out-of-Sample Comparisons of Overfit Models

### 2016-01-23 paper.tex
[#34] Add definition of 'OOS' to body of the paper
This addresses a concern of one of the referees.
[#33] Revise abstract
This commit addresses a point raised by one of the referees about
defining $P$, but it also rewrites the abstract substantially to
try to make it more clear.

\begin{abstract}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the
  number of predictors used by the larger model increase with the
  number of observations so that their ratio remains uniformly
  positive.  Our analysis gives a theoretical motivation for using
  out-of-sample (OOS) comparisons: the DMW OOS test allows a forecaster to
  conduct inference about the expected future accuracy of his or her
  models when one or both is overfit.  We show analytically and
  through Monte Carlo that standard full-sample test statistics can
  not test hypotheses about this performance.  Our paper also shows
  that popular test and training sample sizes may give misleading
  results if researchers are concerned about overfit.  We show that
  $P^2/T$ must converge to zero for the DMW test to give valid
  inference about the expected forecast accuracy, otherwise the test
  measures the accuracy of the estimates constructed using only the
  training sample.  In empirical research, $P$ is typically much
  larger than this.  Our simulations indicate that using large values
  of $P$ with the DMW test gives undersized tests with low power, so
  this practice may favor simple benchmark models too much.

@@

Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use OOS instead of in-sample
comparisons: the DMW OOS test%
\footnote{In this paper, we will refer to the basic OOS $t$-test
  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo simulations
that standard full-sample test statistics can not test hypotheses
about this performance.

>>>>

\begin{abstract}\noindent
  This paper uses dimension asymptotics to study the behavior of
  out-of-sample (OOS) test statistics when they are used to compare
  ``overfit'' linear regression models. Under these asymptotics, the
  number of predictors used by the larger model increases with the
  number of observations so that their ratio remains uniformly
  positive. This analysis gives a theoretical motivation for using
  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
  \textit{Econometrica}) allows a forecaster to conduct inference
  about the models' generalization error, an important measure of
  forecast accuracy that conditions on the models' parameter estimates.
  We show analytically and through Monte Carlo that standard full-sample
  test statistics can not test hypotheses about this measure of performance.
  Our paper also suggests that comparisons of overfit models require small
  OOS test samples. If $P$ denotes the number of observations used for the
  OOS comparison and $T$ the total number of observations, $P^2/T$ must
  converge to zero for the OOS $t$-test to be centered on the model's
  generalization error.

@@

Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use out-of-sample (OOS) instead of in-sample
comparisons: the DMW OOS test%
\footnote{In this paper, we will refer to the basic OOS $t$-test
  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo simulations
that standard full-sample test statistics can not test hypotheses
about this performance.
